---
title: "Importing data"
author: "Sophia Kleist Karlson"
date: "27 okt 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
pacman::p_load(tidyverse, jsonlite, rjson, stringr, dplyr)

setwd("~/Social Transmission Study/Analysis of drawings/")

RStudio.Version() #why this?

```




```{r}
#test <- fromJSON(file = "data/transmission_5CO150x0gvsv_36kQbsUHMv0I/0/0/session.json")
#head(test)

chain <- c()
generation <- c()

data_path <- 'data/transmission_5CO150x0gvsv_36kQbsUHMv0I/' 

chain_ID <- 1
data_path_chain_list <- paste(data_path, chain_ID, "/", sep="")
data_path_chain_list <- paste(data_path_chain_list,'/', sep="")


#data_path_chain <- paste(data_path, 0, "/", sep="")
  
#dir.exists(file.path(paste(data_path, 1, "/", sep="")))

chain_path <- c()
if (dir.exists(file.path(paste(data_path, 0, "/", sep=""))) == TRUE) {
    chain_path <- paste(data_path, 0, "/", sep="")
}


data_path_chain_list

class(dataPath)

file_ID <- 'session'

data_file <- paste(data_path,file_ID,".json",sep="")

class(data_file)

?paste

data_path_chain_list <- c()
data_path_gen_list
data_file_list <- c()
data_flat <- c()


chain <- c()
generation <- c()





chain <- c()
chain_path <- c()
generation <- c()
gen_path <- c()

for (i in 0:1){ # if there are 20 chains
  #data_path_chain[i] <- paste(data_path, i, "/", sep="")
  if (dir.exists(file.path(paste(data_path, i, "/", sep=""))) == TRUE) {
    chain_path[i] <- paste(data_path, i, "/", sep="")
    chain[i] <- paste(chain, i, sep=",")
    for (g in 0:6){ #if there are 7 generations per chain

      if (dir.exists(file.path(paste(chain_path[g], g, "/", sep=""))) == TRUE) {
        gen_path[g] <- paste(chain_path[g], g, "/", sep="")
        #gen <- g
        #chain_gen_df$generation <- g
        #chain_gen_df$chain <- chain
        generation[g] <- paste(generation,g, sep=",")
      }
    }
    
    #chain_gen_df <- data.frame(chain, generation)
  }
}



if (dir.exists(file.path(paste(data_path, 0, "/", sep=""))) == TRUE) {
  chain_path <- paste(data_path, 0, "/", sep="")
  chain <- 0
  if (dir.exists(file.path(paste(chain_path, 0, "/", sep=""))) == TRUE) {
    gen_path <- paste(chain_path, 0, "/", sep="")
    #gen <- g
    generation <- paste(0)
    chain <- paste(0)
    chain_gen_df <- data.frame(chain, generation)
  }
}


    
  
  #data_path_chain_list[i] <- paste(data_path_chain_list, '/', sep="")
  
  for (g in data_path_chain_list) { # or g in 0:6 if there are 7 generations per chain
    data_path_gen_list[g] <- paste(dataPath + i + '/' + g + '/')
    #dataPath[g] <- paste(dataPath, g, '/')
    dataFileList[g] <- paste(dataPathList,fileID,".json",sep="")
    data_flat[g] <- jsonlite::fromJSON(dataFile, flatten=T) 
    source_images <- d1[g]$source_images[[7]]
    source_images$Subject_ID <- d1$subject[0:4]
    
    for (s in 1:4) {
      source_images$Condition[s] <- str_replace_all(source_images$trial_id[s], 'cond_|_stim_\\d+', '')
      source_images$Stim_ID[s] <- str_replace_all(source_images$trial_id[s], 'cond_\\d+|_stim_', '')
      source_images$stim[s] <- str_replace_all(source_images$stimulus[s], './img/test_stim_|.png', '')
    }
    
    
    #data_flat[g] <- paste(d1[g], collapse=NULL)
    #d1[g] <- paste(dataFile, collapse=NULL)
  }



# find source images (are all crammed into node 7)

#add subject id's to the source image dataframe

# extract condition and stim id from "trial_id" and test stim id



# load csv with MSE data
mse7 <- read.csv("logfiles/SimilarityData4.csv")

for (i in 1:14) {
  mse6$Subject_ID[i] <- source_images$Subject_ID[1]
}

# make a test df from mse6 because source_images don't have as many rows right now
test_mse <- mse6[1:4,]

# merge the two dataset
test_2 <- merge(test_mse, source_images)

# Get rid of unneccedary columns
test_2$Source_image <- NULL
test_2$stimulus <- NULL
test_2$X <- NULL
test_2$trial_id <- NULL

# rename "stimulus" to "Source_image"
test_2$Source_image <- test_2$stim
test_2$stim <- NULL

# put columns in the right order
test_2 <- test_2[, c(1, 4, 5, 2, 3, 7, 6)]

```


```{r}
#all the data from the last participant (because it doesn't append the dataframes together)
for (i in 1:length(list_files)){
  file_path <- list_files[i]
  d <- jsonlite::fromJSON(file_path, flatten=T)
}

file_path_1 <- list_files[1]
d1 <- jsonlite::fromJSON(file_path_1, flatten=T)

file_path_2 <- list_files[2]
d2 <- jsonlite::fromJSON(file_path_2, flatten=T)
file_path_3 <- list_files[3]
d3 <- jsonlite::fromJSON(file_path_3, flatten=T)
file_path_4 <- list_files[4]
d4 <- jsonlite::fromJSON(file_path_4, flatten=T)
file_path_6 <- list_files[6]
d6 <- jsonlite::fromJSON(file_path_6, flatten=T)




shift2 <- function(x, n) `length<-`(tail(x, -n), length(x)) 

file_path_7 <- list_files[7]
d7 <- jsonlite::fromJSON(file_path_7, flatten=T) %>% 
  transform(responses = shift2(responses, 1)) %>% 
  filter(is.na(id) + is.na(responses) < 2 ,) %>% 
  select(subject, responses, id, source_images, files.image.path) %>% 
  add_column(Chain = NA) %>% 
  add_column(Generation = NA) %>% 
  add_column(Condition = NA) %>% 
  add_column(Source_image = NA) 

Source_images <- d7$source_images[[2]]

for (s in 1:nrow(Source_images)) {
  for (d in 4:15){
    if (Source_images$trial_id[s] == d7$id[d]){
      d7$Condition[d] <- str_replace_all(Source_images$trial_id[s], 'cond_|_stim_\\d+', '')
      d7$Source_image[d] <- str_replace_all(Source_images$stimulus[s], './img/stim_|.png', '')
    }
  d7$Chain <- str_replace_all(d7$files.image.path[2], '/\\d+/tutorial1.png', '') %>% str_extract('[:digit:]+$')
  d7$Generation <- str_replace_all(d7$files.image.path[2], '/\\d+/|/tutorial1.png', '') %>% str_extract('[:digit:]+$')
  }
}

d7 <- select(d7, subject, Chain, Generation, Condition, Source_image, responses)
d7 <- d7[-c(1:3), ]



```


Loop that works for 1 dataset
```{r}
shift2 <- function(x, n) `length<-`(tail(x, -n), length(x)) 

file_path_7 <- list_files[7]
d7 <- jsonlite::fromJSON(file_path_7, flatten=T) %>% 
  transform(responses = shift2(responses, 1)) %>% 
  filter(is.na(id) + is.na(responses) < 2 ,) %>% 
  select(subject, responses, id, source_images, files.image.path) %>% 
  add_column(Age = NA) %>% 
  add_column(Gender = NA) %>% 
  add_column(Occupation = NA) %>% 
  add_column(Chain = NA) %>% 
  add_column(Generation = NA) %>% 
  add_column(Condition = NA) %>% 
  add_column(Source_image = NA) %>% 
  add_column(Confidence = NA) %>% 
  add_column(Difficulty = NA) %>% 
  add_column(Like = NA) %>% 
  add_column(Experience = NA) 

Source_images <- d7$source_images[[2]]

for (s in 1:nrow(Source_images)) {
  for (d in 4:15){
    if (Source_images$trial_id[s] == d7$id[d]){
      d7$Condition[d] <- str_replace_all(Source_images$trial_id[s], 'cond_|_stim_\\d+', '')
      d7$Source_image[d] <- str_replace_all(Source_images$stimulus[s], './img/stim_|.png', '')
    }
  d7$Chain <- str_replace_all(d7$files.image.path[2], '/\\d+/tutorial1.png', '') %>% str_extract('[:digit:]+$')
  d7$Generation <- str_replace_all(d7$files.image.path[2], '/\\d+/|/tutorial1.png', '') %>% str_extract('[:digit:]+$')
  }
}

d7 <- select(d7, subject, Age, Gender, Occupation, Chain, Generation, Condition, Source_image, Confidence, responses, Difficulty, Like, Experience) 

d7$Like <- str_split_fixed(tail(d7$responses, 3)[1], "\\,",2)[,1] %>% str_replace_all('\\{"post_questionaire_like":', '')
d7$Difficulty <- str_split_fixed(tail(d7$responses, 3)[1], "\\,",2)[,2] %>% str_replace_all('"post_questionaire_difficulty":|\\}', '')

d7$Experience <- tail(d7$responses, 3)[2] %>% str_replace_all('^\\{"Q0":"|"\\}$', '')

d7$Gender <- str_split_fixed(tail(d7$responses, 3)[3], "\\,",3)[,1] %>% str_replace_all('\\{"gender":"|"$', '')
d7$Age <- str_split_fixed(tail(d7$responses, 3)[3], "\\,",3)[,2] %>% str_replace_all('"age":"|"$', '')
d7$Occupation <- str_split_fixed(tail(d7$responses, 3)[3], "\\,",3)[,3] %>% str_replace_all('"occupation":"|"\\}$', '')

d7$Confidence <- str_replace_all(d7$responses, '\\{"confidence":|\\}', '')


d7 <- slice(d7, 1:(n()-3)) 
d7 <- tail(d7,12)

d7$responses <- NULL

```



#Load data
Make a loop for loading the logfiles
```{r}
#specifying data path
data_path <- 'data' 
#creating a list of files
list_files <- list.files(path = data_path,
                         recursive = T,
                         pattern = "session.json$",
                         full.names = T)

list_files
# wmpty data fame with the correct column names
all_data <- data.frame(matrix(ncol = 12, nrow = 0))
x <- c("Subject", "Chain", "Generation", "Condition", "Source_image", "MSE", "Complexity", "Conventionality", "Confidence", "Responses", "Test_part", "RT")#the last three ones I am not completely sure we need 
colnames(all_data) <- x

length(list_files)


#subject_data <- data.frame(matrix(ncol = 1, nrow = 0))
#x <- c("Subject")
#colnames(subject_data) <- x


shift2 <- function(x, n) `length<-`(tail(x, -n), length(x))


#loop that extraxts the data we want
for (i in 1:length(list_files)){
  file_path <- list_files[i]
  d <- jsonlite::fromJSON(file_path, flatten=T) %>% 
    # shift responses one row up
    transform(responses = shift2(responses, 1)) %>% 
    #filter out erows where both id and responses are na
    filter(is.na(id) + is.na(responses) < 2 ,) %>% 
    
    
  
  Source_images <- d7$source_images[[8]]
  for (s in 1:nrow(Source_images)) {
      Source_images$Condition[s] <- str_replace_all(Source_images$trial_id[s], 'cond_|_stim_\\d+', '')
      Source_images$Stim_ID[s] <- str_replace_all(Source_images$trial_id[s], 'cond_\\d+|_stim_', '')
      Source_images$Source_image[s] <- str_replace_all(Source_images$stimulus[s], './img/stim_|.png', '')
      Source_images$Chain <- str_replace_all(d7$files.image.path[8], '/\\d+/tutorial1.png', '') %>% str_extract('[:digit:]+$')
      Source_images$Generation <- str_replace_all(d7$files.image.path[8], '/\\d+/|/tutorial1.png', '') %>% str_extract('[:digit:]+$')
  }
  d <- d %>% 
    rename(Subject = subject, 
           Drawing_ID = id,
           Confidence = responses,
           Source_images = source_images,
           #RT = rt,
           Test_part = test_part,
           Filepath = files.data.path)
    
  
    #mutate(source_images = Source_images[[7]])
    #mutate(Condition = case_when(Drawing_ID==))
    
    #mutate(
     # Condition, Chain,Generation, 
    #) %>% 
    
    select(Subject, Drawing_ID, Source_images, Confidence, Test_part, Filepath)#Condition, Chain, Generation, RT,
  
  if (nrow(all_data) == 0){
    all_data <- d
  } else{
    all_data <- rbind(all_data, d)
  }
}



 
```

to do:
- devide responses into confidence etc.
- make condition row
- 


```{r}

#specifying data path
data_path <- 'data' 
#creating a list of files
list_files <- list.files(path = data_path,
                         recursive = T,
                         pattern = "session.json$",
                         full.names = T)

list_files
# wmpty data fame with the correct column names

all_data <- data.frame(matrix(ncol = 12, nrow = 0))

#x <- c("Subject", "Chain", "Generation", "Condition", "Source_image", "MSE", "Complexity", "Conventionality", "Confidence", "Responses", "Test_part", "RT")#the last three ones I am not completely sure we need 
#colnames(all_data) <- x

length(list_files)



shift2 <- function(x, n) `length<-`(tail(x, -n), length(x)) 


for (i in 1:length(list_files)){
  shift2 <- function(x, n) `length<-`(tail(x, -n), length(x)) 
  file_path <- list_files[i]
  d <- jsonlite::fromJSON(file_path, flatten=T) %>% 
    transform(responses = shift2(responses, 1)) %>% 
    filter(is.na(id) + is.na(responses) < 2 ,) %>%
    select(subject, responses, id, source_images, files.image.path) %>% 
    add_column(Age = NA) %>% 
    add_column(Gender = NA) %>% 
    add_column(Occupation = NA) %>% 
    add_column(Chain = NA) %>% 
    add_column(Generation = NA) %>% 
    add_column(Condition = NA) %>% 
    add_column(Source_image = NA) %>% 
    add_column(Confidence = NA) %>% 
    add_column(Difficulty = NA) %>% 
    add_column(Like = NA) %>% 
    add_column(Experience = NA) %>% 
    
    
    #mutate(Source_images = source_images[[2]])

    select(subject, Age, Gender, Occupation, Chain, Generation, Condition, Source_image, Confidence, responses, Difficulty, Like, Experience) %>% 
    mutate(Like = str_split_fixed(tail(responses, 3)[1], "\\,",2)[,1] %>% str_replace_all('\\{"post_questionaire_like":', ''),
          Difficulty = str_split_fixed(tail(responses, 3)[1], "\\,",2)[,2] %>% str_replace_all('"post_questionaire_difficulty":|\\}', ''),
          Experience = tail(responses, 3)[2] %>% str_replace_all('^\\{"Q0":"|"\\}$', ''),
          Gender = str_split_fixed(tail(responses, 3)[3], "\\,",3)[,1] %>% str_replace_all('\\{"gender":"|"$', ''),
          Age = str_split_fixed(tail(responses, 3)[3], "\\,",3)[,2] %>% str_replace_all('"age":"|"$', ''),
          Occupation = str_split_fixed(tail(responses, 3)[3], "\\,",3)[,3] %>% str_replace_all('"occupation":"|"\\}$', ''),
          Confidence = str_replace_all(responses, '\\{"confidence":|\\}', ''))
  
  
  if (nrow(all_data) == 0){
    all_data <- d
  } else{
    all_data <- rbind(all_data, d)
  }
}


```

    
   for (s in 1:nrow(Source_images)) {
    for (d in 4:15){
      if (Source_images$trial_id[s] == d$id[d]){
        d$Condition[d] <- str_replace_all(Source_images$trial_id[s], 'cond_|_stim_\\d+', '')
        d$Source_image[d] <- str_replace_all(Source_images$stimulus[s], './img/stim_|.png', '')
      }
    d$Chain <- str_replace_all(d$files.image.path[2], '/\\d+/tutorial1.png', '') %>% str_extract('[:digit:]+$')
    d$Generation <- str_replace_all(d$files.image.path[2], '/\\d+/|/tutorial1.png', '') %>% str_extract('[:digit:]+$')
    }
  }
  
  
  
  
  d <- d %>% 
    select(subject, Age, Gender, Occupation, Chain, Generation, Condition, Source_image, Confidence, responses, Difficulty, Like, Experience) %>% 
    mutate(Like = str_split_fixed(tail(responses, 3)[1], "\\,",2)[,1] %>% str_replace_all('\\{"post_questionaire_like":', ''),
          Difficulty <- str_split_fixed(tail(responses, 3)[1], "\\,",2)[,2] %>% str_replace_all('"post_questionaire_difficulty":|\\}', ''),
          Experience <- tail(responses, 3)[2] %>% str_replace_all('^\\{"Q0":"|"\\}$', ''),
          Gender <- str_split_fixed(tail(responses, 3)[3], "\\,",3)[,1] %>% str_replace_all('\\{"gender":"|"$', ''),
          Age <- str_split_fixed(tail(responses, 3)[3], "\\,",3)[,2] %>% str_replace_all('"age":"|"$', ''),
          Occupation <- str_split_fixed(tail(responses, 3)[3], "\\,",3)[,3] %>% str_replace_all('"occupation":"|"\\}$', ''),
          Confidence <- str_replace_all(responses, '\\{"confidence":|\\}', ''))
          
          
          %>% 
    slice(d, 1:(n()-3)) %>% 
    tail(d,12) %>% 
    responses <- NULL %>% 
    rename(Subject = subject)
    
    
    






  d <- d %>% 
    rename(Chain = info.chain,
           Subject = info.subject,
           Generation = info.generation) %>% 
    mutate(Condition_label=
      case_when(
        Condition ==2~"Naming transmission" ,
        Condition ==1~"Pure transmission")) %>% 
      select(test_part, rt, Condition, Condition_label, Subject, Chain, Generation, Language, Hue_source, Saturation_source, Lightness_source, Hue_matched, Saturation_matched, Lighness_matched, Color_label_source, Color_label_matched, Language, basic_colors, creative_name, Hue_color_to_name, Saturation_color_to_name, Lightness_color_to_name, Color_label_naming, responses)
    

  if (nrow(all_data) == 0){
    all_data <- d
  } else{
    all_data <- rbind(all_data, d)
  }

    
#Exstarcting demographics
```{r}
#filtering demographics
demo <- allData %>% 
  filter(test_part == 'demographics') %>% 
  select(Subject, responses)

#Preparing loop
demoData <- data.frame(matrix(ncol = 6, nrow = length(demo$Subject)))
names <- c("Subject","Vision_impairments", "Age", "Gender", "Language_spoken", "Participated_before")
colnames(demoData) <- names
demoData <- left_join(demo, demoData)

#making a loop that extracts all the information from the demographics responses
for (i in 1:length(demo$Subject)){
  matrix <- str_split_fixed(demo[i,2], "\\,",5)
  matrix2 <- str_split_fixed(matrix, "\\:",2)
  demo_df <- as.data.frame(matrix2)
  data_wide <- spread(demo_df, V1, V2)
  
  demoData[i,3] <- as.character(data_wide[1,5])
  demoData[i,4] <- as.character(data_wide[1,1])
  demoData[i,5] <- as.character(data_wide[1,2])
  demoData[i,6] <- as.character(data_wide[1,3])
  demoData[i,7] <- as.character(data_wide[1,4])

  
}  

#Removing punctuations
demoData$Vision_impairments <- gsub('[[:punct:] ]+','',demoData$Vision_impairments)
demoData$Age <- gsub('[[:punct:] ]+','',demoData$Age)
demoData$Gender <- gsub('[[:punct:] ]+','',demoData$Gender)
demoData$Language_spoken <- gsub('[[:punct:] ]+','',demoData$Language_spoken)
demoData$Participated_before <- gsub('[[:punct:] ]+','',demoData$Participated_before)

#Removing responses column
demoData <- demoData %>% select(-responses)

#merge demographics with allData
allData <- merge(allData, demoData)

#fixing some rows
fix <- allData %>% filter(Age == "no")
fix$Age <- fix$Gender
fix$Gender <- fix$Language_spoken
fix$Language_spoken <- fix$Participated_before
fix$Participated_before <- "no"
#and replacing them 
allData <- subset(allData, Age!="no")
allData <- rbind(allData, fix)

```

#Extractin confidence ratings
```{r}
#Rename color labels to English
allData <- allData %>% 
  mutate(Color_label_matched = case_when(
          Color_label_matched == "seed sennepsgul" ~ "seed mustard",
          Color_label_matched == "seed græsgrøn" ~ "seed grass green",
          Color_label_matched == "seed havblå" ~ "seed ocean blue",
          Color_label_matched == "seed mørk rosa" ~ "seed dark rose",
          Color_label_matched == "seed mintgrøn" ~ "seed mint green",
          TRUE ~ Color_label_matched)) %>%
  #subset(Color_label_matched!="seed mint green") %>% 
  mutate(lagged_label = lag(Color_label_matched, n = 1))

#filtering confidence ratings
confidence <- allData %>% 
  filter(test_part == 'confidence') %>% 
  select(Subject, responses, lagged_label) %>%
  na.omit() %>% 
  rename(Color_label_matched = lagged_label,
         Confidence = responses)

confidence$Confidence <- str_replace_all(confidence$Confidence, "..\\bconfidence..", "")
confidence$Confidence <- str_replace_all(confidence$Confidence, "\\}", "")
confidence$Confidence <- as.numeric(confidence$Confidence)

#removing test match
confidence <- subset(confidence, Color_label_matched!="seed mint green")


```

#Making color matching df
Filter rows containing color matching and selecting which rows to keep
+ Creating the column with focal hue values
```{r}
color_matching <- allData %>% 
  filter(test_part == 'matching') %>% 
  select(Subject, Language, Age, Gender, Language_spoken, rt, Condition, Condition_label,  Chain, Generation, Language, Color_label_source, Color_label_matched, Lightness_source, Lighness_matched, Saturation_source, Saturation_matched, Hue_source, Hue_matched) 


#Add 360 when matched hue is between 0 and 20 
# color_matching$Hue_matched <- as.numeric(color_matching$Hue_matched)
# color_matching$Hue_matched <- case_when(color_matching$Hue_matched < 30 ~ color_matching$Hue_matched + 360,
#                                color_matching$Hue_matched > 13 ~ color_matching$Hue_matched)
# color_matching$Hue_source <- case_when(color_matching$Hue_source < 13 ~ color_matching$Hue_source + 360,
#                                color_matching$Hue_source > 13 ~ color_matching$Hue_source)
#Subtract 360 when matched hue is above 360 
# color_matching$Hue_matched <- case_when(color_matching$Hue_matched > 360 ~ color_matching$Hue_matched - 360,
#                                color_matching$Hue_matched < 360 ~ color_matching$Hue_matched)
# color_matching$Hue_source <- case_when(color_matching$Hue_source > 360 ~ color_matching$Hue_source - 360,
#                                color_matching$Hue_source < 360 ~ color_matching$Hue_source)

#Hues of each focal color 
red <- 12.2 + 360
yellow <- 62.4
green <- 136.5
blue <- 193.6
#Hues of each seed color 
red_blue <- 327.55
yellow_red <- 49.85
green_yellow <- 117.98
blue_green <- 179.34
#Add focal hue angles
color_matching <- color_matching %>% 
  mutate(Focal = case_when(
          Color_label_matched == "seed mustard" ~ yellow,
          Color_label_matched == "seed grass green" ~ green,
          Color_label_matched == "seed ocean blue" ~ blue,
          Color_label_matched == "seed dark rose" ~ red)) %>% 
  mutate(Seed = case_when(
          Color_label_matched == "seed mustard" ~ yellow_red,
          Color_label_matched == "seed grass green" ~ green_yellow,
          Color_label_matched == "seed ocean blue" ~ blue_green,
          Color_label_matched == "seed dark rose" ~ red_blue))

#removing test match
color_matching <- subset(color_matching, Color_label_matched!="seed mint green")

#As numeric
color_matching$Seed <- as.numeric(color_matching$Seed)

#Add column with difference between matched hue and focal:
color_matching <- color_matching %>% 
  mutate(
    Dif = Focal - Hue_matched,
    Rel_dif = 100/(Focal - Seed)*Dif,
    Accuracy_hue = abs(Hue_source - Hue_matched),
    Accuracy_sat = abs(Saturation_source - Saturation_matched)
  )

#Adding confidence ratings
color_matching <- left_join(confidence, color_matching)

#As factors cleaned
color_matching$Condition <- as.factor(color_matching$Condition)
color_matching$Chain <- as.factor(color_matching$Chain)
color_matching$Color_label_matched <- as.factor(color_matching$Color_label_matched)
color_matching$Gender <- as.factor(color_matching$Gender)
color_matching$Language <- as.factor(color_matching$Language)

#unique danish
color_matching_danish <- color_matching %>% filter(Language == "Danish")
us <- unique(color_matching$Subject)
usd <- unique(color_matching_danish$Subject)
levels(color_matching$Color_label_matched)

#Writing the CSV file to directory with date of writing automatically generated
write.csv(color_matching, file=paste("color_matching",Sys.Date(), sep = "", ".csv"))


```


#Making color naming df

```{r}
color_naming_df <- allData %>% 
  filter(test_part == 'naming') %>% 
  select(Condition_label, basic_colors, creative_name, Chain, Generation, Subject, Condition, Language, Hue_color_to_name, Saturation_color_to_name, Lightness_color_to_name, Color_label_naming, Vision_impairments, Age, Gender, Language_spoken, Participated_before) 

us <- unique(color_naming_df$Subject)

write.csv(color_naming_df, file=paste("color_naming",Sys.Date(),sep = "", ".csv"))

```

#Making reflective responses df
```{r}

#Reflecting
d_reflect <- allData %>% 
  filter(test_part == 'post-experiment') %>% 
  select(responses, Subject, Language_spoken, Gender, Age)

#Cleaning columns
d_reflect$responses <- str_replace_all(d_reflect$responses, "..\\blanguage..", "") 
d_reflect$responses <- str_replace_all(d_reflect$responses, "\\}", "") 
d_reflect$responses <- str_replace_all(d_reflect$responses, "\\p{quotation mark}", "")

##Remove empty rows
d_reflect$responses <- as.character(d_reflect$responses)
d_reflect$responses[d_reflect$responses==""] <- NA
d_reflect$responses <- as.factor(d_reflect$responses)
d_reflect <- na.omit(d_reflect)


write.csv(d_reflect, file=paste("reflect",Sys.Date(),sep = "", ".csv"))

?count
```





Dummy variable plots
```{r}

dummy_data_generation <- c(1, 2, 3, 4, 5, 6, 7, 1, 2, 3, 4, 5, 6, 7, 1, 2, 3, 4, 5, 6, 7, 1, 2, 3, 4, 5, 6, 7)
dummy_data_condition <- c(1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4, 1, 2, 3, 4)

dummy_data_error <- c(100, 79, 58, 40, 93, 76, 56, 40, 98, 77, 57, 40, 92, 73, 60, 40, 97, 75, 57, 40, 90, 80, 58, 40, 95, 77, 55, 40)

dummy_data_complexity <- c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
dummy_data_complexity <- c(99, 4, 0, 100, 6, 7, 0, 100, 10, 11, 12, 100, 14, 0, 16, 100, 18, 19, 0, 100, 0, 23, 25, 100, 26, 27, 28, 100)

dummy_data <- data.frame(dummy_data_subject_id, dummy_data_chain, dummy_data_generation, dummy_data_condition, dummy_data_complexity, dummy_data_error)


dummy_plotting_complexity <- 
  ggplot(dummy_data, aes(x = dummy_data_generation, y = dummy_data_complexity)) +
  geom_point(aes(color = dummy_data_condition)) +
  labs(title = "Development of complexity over generations across conditions ",
       x = "Generation",
       y = "Complexity", 
       color = "Condition")
dummy_plotting_complexity


dummy_plotting_error <- 
  ggplot(dummy_data, aes(x = dummy_data_generation, y = dummy_data_error)) +
  geom_point(aes(color = dummy_data_condition)) +
  labs(title = "Development of error over generations across conditions ",
       x = "Generation",
       y = "Error", 
       color = "Condition")

dummy_plotting_error

dummy_data_subject_id <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28)
dummy_data_chain <- c(1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 3, 4, 4, 4, 4, 4, 4, 4)


```

