---
title: "Preprocessing"
author: "Sophia Kleist Karlson"
date: "11 nov 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


pacman::p_load(tidyverse, jsonlite, rjson, stringr, dplyr)

setwd("~/Social Transmission Study/Analysis of drawings/")

RStudio.Version() #why this?
```



This loop works
```{r}

#specifying data path
data_path <- 'data' 

#creating a list of files
list_files <- list.files(path = data_path,
                         recursive = T,
                         pattern = "session.json$",
                         full.names = T)

list_files
# wmpty data fame with the correct column names

all_data <- data.frame(matrix(ncol = 1, nrow = 0)) #ncol doesn't actually make a difference

length(list_files)

# function that shifts one column one row up
shift2 <- function(x, n) `length<-`(tail(x, -n), length(x)) 


for (i in 1:length(list_files)){
  shift2 <- function(x, n) `length<-`(tail(x, -n), length(x)) 
  file_path <- list_files[i]
  d <- jsonlite::fromJSON(file_path, flatten=T) %>% 
    transform(responses = shift2(responses, 1)) %>% 
    filter(is.na(id) + is.na(responses) < 2 ,) %>%
    add_column(Age = NA) %>% 
    add_column(Gender = NA) %>% 
    add_column(Occupation = NA) %>% 
    add_column(Chain = NA) %>% 
    add_column(Generation = NA) %>% 
    add_column(Condition = NA) %>%
    add_column(Confidence = NA) %>% 
    add_column(Difficulty = NA) %>% 
    add_column(Like = NA) %>% 
    add_column(Experience = NA) %>% 
    select(subject, Age, Gender, Occupation, Chain, Generation, Condition, source_images, Confidence, responses, Difficulty, Like, Experience, id, files.image.path) %>% 
    #extracting answers from questionaires
    mutate(Experience = tail(responses, 3)[2] %>% str_replace_all('^\\{"Q0":"|"\\}$', ''),
          Gender = str_split_fixed(tail(responses, 3)[3], "\\,",3)[,1] %>% str_replace_all('\\{"gender":"|"$', ''),
          Age = str_split_fixed(tail(responses, 3)[3], "\\,",3)[,2] %>% str_replace_all('"age":"|"$', ''),
          Occupation = str_split_fixed(tail(responses, 3)[3], "\\,",3)[,3] %>% str_replace_all('"occupation":"|"\\}$', ''),
          Confidence = str_replace_all(responses, '\\{"confidence":|\\}', ''),
          Chain = str_replace_all(files.image.path[2], '/\\d+/tutorial1.png', '') %>% str_extract('[:digit:]+$'),
          Generation = str_replace_all(files.image.path[2], '/\\d+/|/tutorial1.png', '') %>% str_extract('[:digit:]+$'),
          Condition = str_replace_all(id, 'cond_|_stim_\\d+', ''))
  
  #extracting difficulty and likability
  if (str_detect(tail(d$responses, 3)[1], '\\{"post_questionaire":\\d+\\}') == TRUE){
    d <- d %>% mutate(Difficulty = tail(responses, 3)[1] %>% str_replace_all('\\{"post_questionaire":|\\}', ''))
  } else {
    d <- d %>% 
      mutate(Difficulty = str_split_fixed(tail(responses, 3)[1], "\\,",2)[,2] %>% str_replace_all('"post_questionaire_difficulty":|\\}', ''), 
      Like = str_split_fixed(tail(responses, 3)[1], "\\,",2)[,1] %>% str_replace_all('\\{"post_questionaire_like":', ''))
  }
  
  # take care of source images, chain, gen and cond
  Source_images <- d$source_images[[2]] %>% rename(id = trial_id)
  d <- merge(d, Source_images)#, sort = FALSE
  
  d <- d %>% 
    mutate(stimulus = str_replace_all(stimulus, './img/stim_|.png', '')) %>% 
    rename(Source_image = stimulus, 
           Subject = subject) %>%  
    select(Subject, Age, Gender, Occupation, Chain, Generation, Condition, Source_image, Confidence, Difficulty, Like, Experience, files.image.path)
  
  if (nrow(all_data) == 0){
    all_data <- d
  } else{
    all_data <- rbind(all_data, d)
  }
}

```


Inspecting that everything looks fine
```{r}

#is.na(all_data)

# These should be numeric
class(all_data$Generation)
class(all_data$Confidence)
class(all_data$Like)
class(all_data$Difficulty)

all_data$Generation <- as.numeric(all_data$Generation)
all_data$Confidence <- as.numeric(all_data$Confidence)
all_data$Like <- as.numeric(all_data$Like)
all_data$Difficulty <- as.numeric(all_data$Difficulty)


# These should be factor
class(all_data$Chain)
class(all_data$Condition)
class(all_data$Source_image)

all_data$Chain <- as.factor(all_data$Chain)
all_data$Condition <- as.factor(all_data$Condition) 
all_data$Source_image <- as.factor(all_data$Source_image)


# These should be character
class(all_data$Subject)
class(all_data$Age)
class(all_data$Gender)
class(all_data$Occupation)



# Checking range of some variables
range(all_data$Chain)
range(all_data$Generation)
range(all_data$Source_image)
range(all_data$Confidence)


# Delete rows from chains with missing drawings (chain 1, 6, 10 and 23)
all_data <- all_data[!all_data$Chain == 1,]
all_data <- all_data[!all_data$Chain == 6,]
all_data <- all_data[!all_data$Chain == 10,]
all_data <- all_data[!all_data$Chain == 11,]
all_data <- all_data[!all_data$Chain == 24,]

#write csv file with ID's and image paths
write.csv(all_data, "data/cleaned_data.csv")
```



Make unique drawing IDs and export their paths in a csv
```{r}

#first, add an "ID" row for individual id's containing chain, generation, condition and source image

all_data <- all_data %>% 
  mutate(Drawing_ID = paste("Chain_", Chain, "_Gen_", Generation, "_Cond_", Condition, "_Source_", Source_image, sep=""))
#all_data$Drawing_ID


#create dataframe with image paths and unique ID's
image_names <- data.frame(matrix(ncol = 1, nrow = nrow(all_data)))

# take image paths from all_data and use as image path column, just take out and rename the first part of the path that is not called the same on my computer:
image_names$image_path <- all_data$files.image.path %>%  str_replace_all('^/experiments/VY53sLXHyJ6H/0G5z021ZWZdA/', 'data/')
#tried this, but it didn't work: ^/[[:alpha:]+]/[[:alnum:]+]/[[:alnum:]+]/\\d+/\\d+/
#the paths look like this: /experiments/VY53sLXHyJ6H/0G5z021ZWZdA/0/0/cond_1_stim_1.png

#take unique drawing ID names
image_names$Drawing_ID <- all_data$Drawing_ID
image_names[,1] <- NULL

source_names <- c("stim_1", "stim_2", "stim_3", "stim_4", "stim_5", "stim_6", "stim_7", "stim_8", "stim_9", "stim_10", "stim_11", "stim_12")
drawing_names <- image_names[,2]

names <- c(drawing_names, source_names)

#write csv file with ID's and image paths
write.csv(names, "data/all_drawing_names.csv")
write.csv(image_names, "data/Drawing_IDs.csv")


```


NOW, THE PYTHON IMAGE PROCESSING SCRIPT IS RUN, WHICH CREATES THE COMPLEXITY_COMPARISON.CSV THAT IS USED BELOW


# comparing complexity of orignal and blurred images
```{r}

# read complexity data and delete the first unnecessary column
complexity_data <- read.csv("data/complexity_comparison.csv")
complexity_data$X <- NULL


#check class of complexity measures - they need to be numeric
class(complexity_data$Complexity_original)
class(complexity_data$Complexity_convolution)

complexity_data$Complexity_original <- as.numeric(complexity_data$Complexity_original)
complexity_data$Complexity_convolution <- as.numeric(complexity_data$Complexity_convolution)


# make a column with the rato of complexity between the blurred and original images
complexity_data <- complexity_data %>% mutate(ratio = Complexity_convolution/Complexity_original)
range(complexity_data$ratio)


#why does this not work?
complexity_data <- complexity_data %>% mutate(mean_comp = mean(Complexity_original, Complexity_convolution))


# correlation between the ratio and the comlexity of orignals
cor(complexity_data$ratio, complexity_data$Complexity_original) #-0.1768 - pretty weak correlation, but still there
cor(complexity_data$ratio, complexity_data$Complexity_convolution) # -0.1259 - even weaker

```


Merge complexity dataframe with all_data
```{r}
all_data_2 <- merge(all_data, complexity_data)

all_data_2$Complexity <- all_data_2$Complexity_convolution

all_data_2$Complexity_convolution <- NULL


#write csv file with complexity scores
write.csv(all_data_2, "data/data_w_complexity.csv")
```



importing conventionality data
```{r}

#specifying data path
data_path_m <- 'data/mturk' 

#creating a list of files
list_files_m <- list.files(path = data_path_m,
                         recursive = T,
                         pattern = "session.json$",
                         full.names = T)

data_path_m
list_files_m
# wmpty data fame with the correct column names

all_data_m <- data.frame(matrix(ncol = 1, nrow = 0)) #ncol doesn't actually make a difference

length(list_files_m)


# extract all mturk files and 
for (i in 1:length(list_files_m)){
  file_path_m <- list_files_m[i]
  d_m <- jsonlite::fromJSON(file_path_m, flatten=T) %>% 
    select(drawing_id, button_pressed, completion_code) %>% 
    rename(Drawing_ID = drawing_id,
           Conventionality = button_pressed) %>% 
    filter(is.na(Drawing_ID) + is.na(completion_code) < 2 ,)
  if (nrow(all_data_m) == 0){
    all_data_m <- d_m
  } else {
    all_data_m <- rbind(all_data_m, d_m)
  }
}

class(all_data_m$Conventionality)
all_data_m$Conventionality <- as.numeric(all_data_m$Conventionality)
mean(all_data_m$Conventionality)
sd(all_data_m$Conventionality)
range(all_data_m$Conventionality)

completion_codes <- all_data_m$completion_code 
completion_codes <- completion_codes[complete.cases(completion_codes)]




#merge conventionality scores with all_data
all_data_w_convention <- merge(all_data, all_data_m)
all_data_w_conv_comp <- merge(all_data_2, all_data_m)

all_data_w_convention$completion_code <- NULL 
all_data_w_conv_comp$completion_code <- NULL 

#write csv files
write.csv(all_data_w_convention, "data/all_data_w_convention.csv") # all data with conventionality scores
write.csv(completion_codes, "data/completion_codes.csv") # completion codes
write.csv(all_data_m, "data/conventionality_data.csv") # conventionality scores
write.csv(all_data_w_conv_comp, "data/all_data_w_conv_comp.csv") # all data with conventionality and complexity scores


```




looking at conventionality from the last 35 trials for each participant
```{r}
all_data_m1 <- data.frame(matrix(ncol = 1, nrow = 0)) #ncol doesn't actually make a difference

for (i in 1:length(list_files_m)){
  file_path_m <- list_files_m[i]
  d_m <- jsonlite::fromJSON(file_path_m, flatten=T) %>% 
    #select(drawing_id, button_pressed, completion_code) %>% 
    rename(Drawing_ID = drawing_id,
           Conventionality = button_pressed) %>% 
    filter(is.na(Drawing_ID) + is.na(completion_code) < 2 ,)
  if (nrow(all_data_m1) == 0){
    all_data_m1 <- d_m
  } else {
    all_data_m1 <- rbind(all_data_m1, d_m)
  }
}

all_data_m1$Conventionality <- as.numeric(all_data_m1$Conventionality)
class(all_data_m1$Conventionality)

conv_last35 <- all_data_m1 %>% 
  group_by(subject) %>%   
  slice(tail(row_number(), 35)) %>% 
  select(Conventionality, subject) %>% 
  as.data.frame()

mean(conv_last35$Conventionality) #4.606845 - so basically the same as the overall mean
sd(conv_last35$Conventionality) #2.965397 - also basically the same - both mean and sd go up 0.1 but it doesn't seem problematic
```




making a local source drawing list for calculating MSE
```{r}
drawing_orig <- all_data %>% select(Chain, Generation, Source_image, Drawing_ID)
drawing_copy <- drawing_orig

shift <- function(x, n) `length<-`(tail(x, +n), length(x))


drawing_orig1 <- drawing_orig

for (i in drawing_orig1){
  drawing_orig1 <- drawing_orig1 %>% transform(Drawing_ID = shift(Drawing_ID, 1))
  if (nrow(all_data) == 0){
    all_data <- drawing_orig1
  } else{
    all_data <- rbind(all_data, drawing_orig1)
  }
}



class(drawing_copy$Generation)

drawing_copy$Chain <- as.character(drawing_copy$Chain)
drawing_copy$Chain <- as.numeric(drawing_copy$Chain)

drawing_copy$Source_image <- as.character(drawing_copy$Source_image)
drawing_copy$Source_image <- as.numeric(drawing_copy$Source_image)

drawing_orig$Chain <- as.character(drawing_orig$Chain)
drawing_orig$Chain <- as.numeric(drawing_orig$Chain)

drawing_orig$Source_image <- as.character(drawing_orig$Source_image)
drawing_orig$Source_image <- as.numeric(drawing_orig$Source_image)



for (i in 1:nrow(drawing_orig)){
  if (drawing_copy$Generation[i] == 0){
    drawing_orig$Drawing_ID[i] <- paste("stim_",drawing_copy$Source_image[i], sep="")
  } else if (drawing_orig$Drawing_ID[i] == drawing_copy$Drawing_ID[i]){
    drawing_orig$Drawing_ID[i] <- drawing_copy$Drawing_ID[i-12]
  }
}

drawing_ids_copy_orig <- data.frame(matrix(ncol = 1, nrow = 1680))
drawing_ids_copy_orig$Orig_ID <- drawing_orig$Drawing_ID
drawing_ids_copy_orig$Copy_ID <- drawing_copy$Drawing_ID
drawing_ids_copy_orig[,1] <- NULL

write.csv(drawing_ids_copy_orig, "data/drawings_source_copy.csv")
write.csv(drawing_orig, "data/drawings_source.csv")
write.csv(drawing_copy, "data/drawings_copy.csv")

```

  
